---
title: "NCAA Division I Basketball Tournament History"
output: 
  html_document:
    theme: cerulean
    code_folding: hide
---

```{r, include=FALSE}
library(mosaic)
library(DT) 
library(knitr)
library(pander)
library(car)
library(plyr)
library(dplyr)
```

```{r}
Allgames <- read.csv("./Pre 2018 History.csv",header=TRUE, stringsAsFactors = FALSE)
teamconf <- read.csv("./teamconf.csv",header=TRUE, stringsAsFactors = FALSE)
AGTC <- merge(Allgames,teamconf, by.x = "Winner", by.y = "Team", all.x = TRUE)
colnames(AGTC)[colnames(AGTC)=="Conference"] <- "WConf"
AGTCC <- merge(AGTC,teamconf, by.x = "Loser", by.y = "Team", all.x = TRUE)
colnames(AGTCC)[colnames(AGTCC)=="Conference"] <- "LConf"
mycolumns<-c(3:7,2,12,8,9,1,13,10,11)
AGTCCS<-AGTCC[mycolumns]
AGTCCS$SeD <- AGTCCS$wSeed-AGTCCS$LSeed
AGTCCS$ScD <- AGTCCS$WScore -AGTCCS$LScore
AGTCCS$Upset<-paste(AGTCCS$wSeed, AGTCCS$LSeed, sep=" over ")
```
## {.tabset .tabset-fade}

### Overview

In 1985, the NCAA expanded their Division I basketball tounament to a 64 team single elimination tournament. Since that time there have been 2117 games (including some play in games).

### All Games

```{r}
datatable(Allgames, extensions = "Responsive",options=list(lengthMenu = c(10,25,68)))
```

### Seed History

Some interesting trends have occured in the past 33 years.

* A number 5 seed has never won a chapionship even though a 6, 7, and 8 seed have. 

* The 10, 11, and 12 seeds have faired much better than the 9 seeds.

* No 16 seed has ever beaten a 1 seed.

* The number 1 seeds have collected the majority of the championships.

```{r, warning=FALSE}
Allgames$Round<-factor(Allgames$Round, levels=c("Play-in", "64", "32","16","8","4","Champ"))
SH<-table(Allgames$wSeed,Allgames$Round)
rownames(SH)<-c("Seed 1","Seed 2","Seed 3","Seed 4","Seed 5","Seed 6","Seed 7","Seed 8","Seed 9","Seed 10","Seed 11","Seed 12","Seed 13","Seed 14","Seed 15","Seed 16")
pander(SH)
```

### Upsets
```{r}
upsets<-subset(AGTCCS, SeD>=4)
pander(table(upsets$Upset))

pander(table(upsets$WConf))
```

