---
title: "Harmon Important Code"
output: 
  html_document:
    theme: cerulean
    code_folding: hide
    #toc: true
    #toc_float: true
---
```{r, include=FALSE}
library(mosaic)
library(DT) 
library(knitr)
library(pander)
library(car)
library(plyr)
library(dplyr)
```

## Dataframes {.tabset .tabset-fade}

### Nothing

### Read

Read and write a csv dataset after setting a working directory
```{r}
Movies31<-read.csv("./Data/movies31.csv", header=TRUE, stringsAsFactors = FALSE)
CPI <- read.csv("./Data/CPI1914to2017.csv", header=TRUE, stringsAsFactors = FALSE)
#write.csv(Movies31, file = "./Data/MoviesOut.csv")
```

### Subsets
```{r}
# slim down to 4 ratings
mr4<-subset(Movies31, rating %in% c("G","PG","PG-13","R"), )

# movies G-rated and > $100 Mil
GoodFamily <- subset(Movies31, rating == "G" & gross >= 100000000)

# Change budget = 0 to budget = NA
Movies.wb <- Movies31
MB <- Movies.wb$budget
MB[MB == 0] <- NA 
Movies.wb$budget <- MB

# Filter out budget = NA
Movies.wb <- subset(Movies.wb, !is.na(budget))

#re-sort columns
mycolumns<-c(15,9,7,2,5,8,10,3,1,6,4,13,11,12,14)
Movies.Sorted<-Movies31[mycolumns]

#re-sort rows
Movies.Sorted <- Movies.Sorted[order(Movies.Sorted$released),]

# Cut a Quantitative Variable into categories
Movies.Sorted$buster <- cut(Movies.Sorted$gross, breaks = c(0,100000,1000000,10000000,100000000,1000000000), 
                            labels = c("Size 1","Size 2","Size 3","Size 4","Size 5"))

airquality$Season<-mapvalues(airquality$Month,5:9,c("Spr",rep("Sum",3),"Fall"))

```

### Summary
```{r}
datatable(GoodFamily, extensions = "Responsive",options=list(lengthMenu = c(3,10,30)))
pander::pander(favstats(budget~country, data = GoodFamily))
GbyC<-favstats(budget~country, data = GoodFamily)
knitr::kable(GbyC)
pander::pander(sum(budget~country, data = GoodFamily))
```

### Convert
```{r}
Movies31$year <- as.factor(Movies31$year)
Movies31$year <- as.integer(as.character(Movies31$year))

Movies.Sorted[5:6] <- lapply(Movies.Sorted[5:6], function(x) as.factor(x))
```

### Vlookup
```{r}
movies2017<-merge(Movies.wb,CPI, by.x = "year", by.y = "Year", all.x = TRUE)
movies2017$Newbudget<-movies2017$budget*movies2017$Factor
```

## Categorical (Qualitative) Data {.tabset .tabset-fade}

### Nothing

### Bar Charts
```{r}
cbust<-table(Movies.Sorted$buster)
barplot( cbust, col=c("gray84","gray44") ,beside=TRUE , legend.text=TRUE )
mscore<-median(score~buster, data = Movies.Sorted)
barplot(mscore, col=c("blue","gold") ,beside=TRUE , legend.text=TRUE )

Movies.Sorted$rating <- as.character(Movies.Sorted$rating)

mrs4<-subset(Movies.Sorted, rating %in% c("G","PG","PG-13","R"), )
counts <- table(mrs4$rating, mrs4$buster)
barplot(counts, main="Movie Distribution \nby Rating and Blockbuster Size", xlab = "Blockbuster size", col = c("darkblue","red","orange","green"), legend = rownames(counts), beside=TRUE)

```

### Table
```{r}
Smovie<-subset(mr4, genre %in% c("Comedy","Action","Drama"))
pander(table(Smovie$genre,Smovie$rating))
```

## Graphical Summaries {.tabset .tabset-fade}

### Nothing

### Scatterplot
```{r}
GoodFamily$budget <- as.integer(GoodFamily$budget)
plot(gross~budget, data = GoodFamily, xlab="Movie Budget", ylab="Gross Revenue", col="gray", pch=19,
     main="G-Rated High Grossing Movies\n1986 through 2016")
abline(lm(gross~budget, data = GoodFamily))
BestGF<-subset(GoodFamily, budget>=median(GoodFamily$budget))
points(gross~budget, data = BestGF, col="steelblue", pch=8)
abline(v=median(GoodFamily$budget), lty=5, col="red", lwd=2)
```

### Histogram
```{r}
hist(Movies.wb$budget, xlab="Budget in Dollars", col="orange", main="")
title("Reported Budgets for movies", line=2)
title("1986-2016", line=1)
```

### boxplot
```{r}
boxplot(budget~rating, data=Movies.wb, ylab="MPAA Rating", xlab="Bugdet in Dollars", 
        col=c("gray","orangered"), main="",
        horizontal=TRUE)
title("Reported Budgets for movies", line=2)
title("1986-2016", line=1)
```

### dotplot
```{r}
stripchart(budget~genre, data=GoodFamily, method="stack" ,ylab="Genre", xlab="Budget in Dollars", 
           main="G-Rated High Grossing Movies\n and Their Budgets\n1986 through 2016", col="sienna", pch=16)  
```



## Inference {.tabset .tabset-fade}

### Nothing

### t-Test

Do R-Rated movies have a significantly greater mean IMDB score than other ratings (G, PG, or PG-13)?

$$
{ H }_{ 0 }:{ \mu  }_{ R:Score }={ \mu  }_{ other:Score }\\ { H }_{ a }:{ \mu  }_{ R:Score }>{ \mu  }_{ other:Score}
$$
```{r}
mrs4$R<-mrs4$rating

RTF <- mrs4$R
RTF[RTF != "R"] <- FALSE
RTF[RTF == "R"] <- TRUE 
mrs4$R <- RTF
```

#### Sample Statistics
```{r}
pander::pander(favstats(score~R, data = mrs4))
```


```{r}
R<-subset(mrs4, R %in% TRUE) 
notR<-subset(mrs4, R %in% FALSE)
par(mfrow=c(1,2))
qqPlot(R$score, xlab = "Ranked Z Scores", ylab = "IMDB Score", main = "R-rated Movies")
qqPlot(notR$score, xlab = "Ranked Z Scores", ylab = "IMDB Score", main = "non-R-rated Movies")
```

#### Assumptions
1. These samples **can** be assumed to be representative of the population movies of this type.
2. According to the QQ-Plots these samples appear to be **not** normal enough.

#### Independent 2 sample t-Test
```{r}



ttp<-t.test(R$score,notR$score, mu = 0, alternative = "greater", conf.level = 0.95)$p.value
tts<-t.test(R$score,notR$score, mu = 0, alternative = "greater", conf.level = 0.95)$statistic
ttdf<-t.test(R$score,notR$score, mu = 0, alternative = "greater", conf.level = 0.95)$parameter

U<-abs(tts)+1
L<-U*(-1)

tcv<-qt(.95, ttdf)



# Create data for the area to shade
TX<-seq(tts,U,.01)
cord.x <- c(tts,TX,U) 
cord.y <- c(0,dt(TX,ttdf),0) 

# Make a curve
curve(dt(x,ttdf), xlim=c(L,U), main="t-Test for the IMDB score of R-rated movies \ncompared to scores of other rated movies", xlab = "") 

# Add the shaded area.
polygon(cord.x,cord.y,col='skyblue')
abline(v=tts, lty=5, col="red", lwd=2)
abline(v=tcv, lty=5, col="blue", lwd=2)
text(tcv,.39,"Critical Value", col="blue")
text(tts,.37,"Test Statistic", col="red")

pander(t.test(R$score,notR$score, mu = 0, alternative = "greater", conf.level = 0.95))

```

* The Test Statistic **(`r tts`)** is greater than the Critical Value **(`r tcv`)**
* The p-value **(`r ttp`)** is smaller than the Level of Significance **$\alpha = .05$**

Therefore, there is **sufficient evidence** to conclude that R-rated movies have a higher average IMDB score than other movies.

### Wilcoxon Signed-Rank Test {.tabset .tabset-fade .tabset-pills}

```{r}
favstats(score~year, data = mrs4)
wilcox.test(score~rating, data = mrs4, subset = rating %in% c("R","G"))
t.test(score~rating, data = subset(mrs4, rating %in% c("R","G")))
```
 















