---
title: "Student Housing Costs"
output: 
  html_document:
    theme: cerulean
    code_folding: hide
    toc: true
    toc_float: true
---


```{r, include=FALSE, r, echo=FALSE}
library(mosaic)
library(DT) 

Rent <- read.csv("./Data/Rent.csv", header=TRUE)
FRent <- subset(Rent, !is.na(Cost))
FRent <- subset(FRent, Gender=="F")
mycolumns<-c(1:8,12,15,16)
FRent<-FRent[mycolumns]
```



## Background

Stephanie[^1] is a student that will be starting school at BYU-Idaho next semester. Here is a copy of the email request for information that she sent.

"Hi. My name is Stephanie. I would like to learn about what housing options I have for living at BYU-Idaho next semester. It will be my first semester there, so I would like to find something that is close to campus and around $300 a month in rent. I'm not too picky on roomates, but I would like somewhere that has a lot of people around so I can get to know as many people as possible. Thanks in advance!"

Here is the list of `r nrow(FRent)` female apartments that list their semester rent on the [BYU-Idaho Housing Website](https://web.byui.edu/tis/search).

### Dataset of Female Housing
```{r, echo=FALSE}
datatable(FRent,extensions = "Responsive", options=list(lengthMenu = c(3,10,30)))
```

## Analysis
Stephanie has suggested that she has two criteria when choosing and aparment complex.

* Budget \$300 per month or \$970 for a 14-week semester
* An aprtment complex with a lot of people

### Summary statistics of Female Housing Costs
```{r, echo=FALSE}
favstats(~Cost, data=FRent)
```
### Summary statistics of Number of Residents
```{r, echo=FALSE}
favstats(~Residents, data=FRent)
```

### Graphical Representation of the Results
Because of Stephanie's criteria, I have eliminated the extreme 25% of complexes 

* Fewer than 23 residents
* Rent greater than 1277
```{r, echo=FALSE}

OFRent<-FRent[order(FRent$Cost),]
OFRent$size<-cut(OFRent$Residents, breaks = c(0,22,92,210,999), 
                 labels=c("", "24 to 92", "93 to 210","211 to 636"))

OFRentR<-subset(OFRent, size!="")
OFRentRC<-subset(OFRentR, Cost<1277)

OFRentRC$color[OFRentRC$size=="24 to 92"]<-"blue"
OFRentRC$color[OFRentRC$size=="93 to 210"]<-"green"
OFRentRC$color[OFRentRC$size=="211 to 636"]<-"black"

rownames(OFRentRC)<-OFRentRC$Apartment
dotchart(OFRentRC$Cost,labels=row.names(OFRentRC),cex=.7,groups= OFRentRC$size,
         main="Female Housing Costs \nGrouped by Number of Residents",
         xlab="Cost per Semester", gcolor="black", color=OFRentRC$color)
```


## Interpretation

Stephanie can use this graphic to narrow her search. She says that cost and size of the complex are he criteria; but, she may want research other aspects of these `r nrow(OFRentRC)` complexes for intangibles not contained in the dataset.




[^1]: Note that Stephanie is a fictional character who is based on real experiences of many faculty and staff here at BYU-Idaho.
