---
title: "Student Housing Costs"
output: 
  html_document:
    theme: cerulean
    code_folding: hide
    toc: true
    toc_float: true
---


```{r, include=FALSE, r, echo=FALSE}
library(mosaic)
library(DT) 
            # If you get an error stating: 
            # Error in library(DT): there is no package called 'DT'
            # You will need to run: install.packages("DT") 
            # in your Console, then try "Knit HTML" again.
Rent <- read.csv("../Data/Rent.csv", header=TRUE)
View(Rent)
RentWH <- subset(Rent, Gender=="F")

View(RentWH)
mycolumns<-c(1:8,12,15,16)
rentWHsmall<-RentWH[mycolumns]
View(rentWHsmall)

```



## Background

Stephanie[^1] is a student that will be starting school at BYU-Idaho next semester. Here is a copy of the email request for information that she sent.

"Hi. My name is Stephanie. I would like to learn about what housing options I have for living at BYU-Idaho next semester. It will be my first semester there, so I would like to find something that is close to campus and around $300 a month in rent. I'm not too picky on roomates, but I would like somewhere that has a lot of people around so I can get to know as many people as possible. Thanks in advance!"

The data from the [BYU-Idaho Housing Website](https://web.byui.edu/tis/search) has data from all the BYUI approved housing. 

For your convenience, the first three observations of a dataset pulled from the BYUI website are shown in the following table. There are a total of `r nrow(rentWHsmall)` observations in the dataset.The dataset has been filtered to just show female housing. However, 2 of the housing complexes have not listed there semester rental cost.

<!-- Hint, you should probably subset the Rent dataset to only show the "Approved Women's Housing" since Stephanie won't be interested in Male Housing options. Also, you can edit this background however you wish when completing your analysis. Notice how this text in green doesn't show up in the HTML output because we used the HTML comment tags around this text. --> 

### Dataset of Female Housing

```{r, echo=FALSE}
datatable(rentWHsmall, options=list(lengthMenu = c(3,10,30)))
```


## Analysis

### Summary statistics of Female Housing Costs
```{r, echo=FALSE}
favstats(~Cost, data=rentWHsmall)
```
### Graphical Description of Female Housing Costs
```{r, echo=FALSE}
hist(rentWHsmall$Cost, col="steelblue", main="BYUI Appoved Female Housing Costs", xlab="Cost per Semester")
boxplot(rentWHsmall$Cost, horizontal=TRUE, col = "steelblue", xlab="Cost per Semester")
```



## Interpretation

Stephanie says she would like to budget \$300 per month; in a 14 week semester that would mean she is looking for about \$970 per semester. If she is firm on that number she will be limited to these apartments:

### Stephanie's options by price
```{r, echo=FALSE}
Srentprice<-subset(rentWHsmall, Cost<=970)
Scol<-c(1,5:8,10)
Srentprice<-Srentprice[Scol]
View(Srentprice)
datatable(Srentprice, options=list(lengthMenu = c(3,10,30)))
```


### More considerations
Stephanie's other requirement is that she would like to be around a lot of people. This could mean a lot of people in the housing complex or a housing complex that is near campus. Of the apartment complexes that meet the price requirements, distance does not vary that much; the size of the housing complexes vary a great deal. 

### Final Suggestion
Based off of Stephanie's criteria, my suggestion is that Stephanie consider these three complexes:

```{r, echo=FALSE}
SH<-subset(Srentprice, Residents>=80)

View(SH)
datatable(SH, options=list(lengthMenu = c(3,10,30)))
```





[^1]: Note that Stephanie is a fictional character who is based on real experiences of many faculty and staff here at BYU-Idaho.
