---
title: "Kids Feet Length t-Test"
output: 
  html_document:
    theme: cerulean
    code_folding: hide
    toc: true
    toc_float: true
---

```{r, include=FALSE}
library(mosaic)
library(DT)
library(pander)
library(car)
library(ggplot2)
```

```{r, eval=FALSE, include=FALSE}
# Run this in your Console to see the data.
View(KidsFeet)
KidsFeet<-KidsFeet
?KidsFeet
```

<!-- Instructions

1. Use the KidsFeet dataset in R to come up with a question that can be answered with a t Test (One Sample, Paired Samples, or Independent Samples).

2. Establish why the question is interesting. State the question in written form as well as with a statistical "null" and "alternative" hypothesis.

3. Clearly answer your question using statistics. Be sure to compute a p-value and provide supporting numerical and graphical summaries. Also be sure to establish whether or not the requirements of your t test have been satisfied. (See the Math 325 Notebook for details.)

-->

## Background

These [data](https://webmailbyui-my.sharepoint.com/:x:/g/personal/harmkenn_byui_edu/Ee2RRg5H3RZIl1tfeK9QUh8BgbujF0r_jXZipv8JfO6OKA?e=5I4L5K) were collected by a statistician, Mary C. Meyer, in a fourth grade classroom in Ann Arbor, MI, in October 1997. They are a convenience sample — the kids who were in the fourth grade.

**Question:** Is the average foot length of fourth graders born in 1987 larger than the average foot length of the younger fourth graders born in 1988?

**Hypotheses**
$$
{ H }_{ 0 }:{ \mu  }_{87Length}={ \mu  }_{88Length}\\ { H }_{ a }:{ \mu  }_{87Length}>{ \mu  }_{88Length}
$$


## Analysis

### Compare the Lengths of Feet for 4th Graders born in '87 and '88
```{r}
KidsFeet$birthyear<-as.factor(KidsFeet$birthyear)
pander::pander(favstats(length~birthyear, data = KidsFeet))
ggplot(data = KidsFeet, aes(x = birthyear, y = length)) + geom_boxplot()  + aes(colour = birthyear) + labs(title = "Foot Length of Sample 4th Graders\nby Birth Year") + coord_flip() +labs(y="Foot Length",x="Birth Year")+ theme(plot.title = element_text(hjust = 0.5))


Y87<-subset(KidsFeet, birthyear %in% 87)
par(mfrow=c(1,2))
qqPlot(Y87$length, xlab = "Ranked Z Scores", ylab = "Foot Length (cm)", main = "'87 Kids")


Y88<-subset(KidsFeet, birthyear %in% 88)
qqPlot(Y88$length, xlab = "Ranked Z Scores", ylab = "Foot Length (cm)", main = "'88 Kids")
```

### Assumptions
1. These samples **cannot** be assumed to be representative an any significant population because it is a convenience sample.
2. According to the QQ-Plots these samples appear to be normal enough.


### Independent 2 sample t-Test
Using a **level of significance: ** $\alpha = .05$
```{r}


ttp<-t.test(Y87$length,Y88$length, mu = 0, alternative = "greater", conf.level = 0.90)$p.value
tts<-t.test(Y87$length,Y88$length, mu = 0, alternative = "greater", conf.level = 0.90)$statistic
ttdf<-t.test(Y87$length,Y88$length, mu = 0, alternative = "greater", conf.level = 0.90)$parameter

U<-abs(tts)+1
L<-U*(-1)

tcv<-qt(.95, ttdf)

# Create data for the area to shade
TX<-seq(tts,U,.01)
cord.x <- c(tts,TX,U) 
cord.y <- c(0,dt(TX,ttdf),0) 

TCX<-seq(tcv,U,.01)
cord.x1 <- c(tcv,TCX,U) 
cord.y1 <- c(0,dt(TCX,ttdf),0) 

# Make a curve
curve(dt(x,ttdf), xlim=c(L,U), main="t-Test for the Length of Feet \nold 4th Graders vs young 4th Graders", xlab = "") 

# Add the shaded area.

polygon(cord.x1,cord.y1,col='#0000FF64')
#transred<-rgb(255,0,0,max=255,alpha=100,names="transred")
polygon(cord.x,cord.y,col='#FF000064')
abline(v=tts, lty=5, col="red", lwd=2)
abline(v=tcv, lty=5, col="blue", lwd=2)
text(tcv,.39,"Critical Value", col="blue")

text(tts,.37,"Test Statistic", col="red")
text(tts+.4,.01,"p-value", col="red")

pander(t.test(Y87$length,Y88$length, mu = 0, alternative = "greater", conf.level = 0.95))
# pander(t.test(length~birthyear, data = KidsFeet, mu = 0, alternative = "greater", conf.level = 0.95))


```

## Interpretation

* The Test Statistic **(`r tts`)** is greater than the Critical Value **(`r tcv`)**
* The p-value **(`r ttp`)** is smaller than the Level of Significance **$\alpha = .05$**

Therefore, there is **sufficient evidence** to conclude that 4th Graders born in '87 have a larger mean foot size than 4th Graders born in '88.

