---
title: "Cadillac Deville Prices"
output: 
  html_document:
    theme: cerulean
    code_folding: hide
---

```{r, include=FALSE}
library(mosaic)
library(DT) 
library(knitr)
library(pander)
library(car)
library(plyr)
library(dplyr)
options(scipen = 999)
```


## {.tabset .tabset-fade}

### Overview

**Context**

In this study, I will be looking at the relationship between the selling price of Cadillac Devilles and the mileage on those Cadillacs.


**The Study**

To perform this study, I will use a sample of 30 Cadillac Devilles in three different Trim styles.

```{r}
CarPrices <- read.csv("../Data/CarPrices.csv", header=TRUE, stringsAsFactors = FALSE)
DevillePrice <- subset(CarPrices, Model == "Deville")
pander(table(DevillePrice$Trim))
```

More specifically I will be analyzing the depreciation rates of the different Trim Styles.

1. Is the depreciation rate for the `DHS Sedan 4D` trim style different than 0? Is there significant depreciation from mileage?
$$
H_0:\beta_1=0\\H_a:\beta_1\neq0
$$
2. Is the depreciation rate for the `DTS Sedan 4D` trim style different than `DHS Sedan 4D`? Is there significant depreciation from mileage?
$$
H_0:\beta_4=0\\H_a:\beta_4\neq0
$$
3. Is the depreciation rate for the `Sedan 4D` trim style different than `DHS Sedan 4D`? Is there significant depreciation from mileage?
$$
H_0:\beta_5=0\\H_a:\beta_5\neq0
$$

**The Data**

```{r}

datatable(DevillePrice, extensions = "Responsive",options=list(lengthMenu = c(5,30)))
```

### Analysis

#### Analysis

```{r}
lmcd <- lm(Price ~ Mileage + Trim + Mileage:Trim, data=DevillePrice)


palette(c("blue","red","green"))
plot(Price~Mileage,data=DevillePrice,
     col=as.factor(DevillePrice$Trim),pch=16,
     xlab="Mileage at Time of Sale", ylab="Selling Price")
b<-lmcd$coefficients

abline(b[1], b[2], col="blue")
abline(b[1]+ b[3],b[2]+ b[5], col="red")
abline(b[1]+ b[4],b[2]+ b[6], col="green")
legend("topright",c("DHS Sedan 4D","DTS Sedan 4D","Sedan 4D"), lty=1, lwd=5, col=palette(), cex=0.7, title="Trim")
```

It appears that each Trim model has different predicted new price and different depreciation.

I will test to see if there is evidence to suggest that the the trim model have different linear models.

#### Inference

```{r}
pander(lmcd)
```

The test of multiple linear regression confirms what the scatter-plot shows; these three models are not all the same.

This is the Price:Mileage Model for all three Trims Styles:

$\quad Y_{i} = \text{Sales Price}$
$\quad X_{i1} = \text{Mileage}$
$\quad X_{i2} = \left\{\begin{array}{ll} 1, & \text{if Trim} = \text{DTS Sedan 4D} \\ 0, & \text{if Trim}\neq \text{DTS Sedan 4D} \end{array}\right.$
$\quad X_{i3} = \left\{\begin{array}{ll} 1, & \text{if Trim} = \text{Sedan 4D} \\ 0, & \text{if Trim}\neq \text{Sedan 4D} \end{array}\right.$

$$\underbrace{Y_i}_{Price}=\beta_0+\beta_1\underbrace{X_{i1}}_{Mileage}+\beta_2{X_{i2}}+\beta_3{X_{i3}}+\beta_4{X_{i1}X_{i2}}+\beta_5{X_{i1}X_{i3}}+\epsilon_i $$

$\hat{ Y }_{ i }=$ `r b[1]` + `r b[2]` ${ X }_{ i1 }+$ `r b[3]` ${ X }_{ i2 }+$ `r b[4]` ${ X }_{ i3 }+$ `r b[5]` ${ X }_{ i1 }{ X }_{ i2 }+$ `r b[6]` ${ X }_{ i1 }{ X }_{ i3 }$


### Assumptions

1. **Linear Relation**: Seems Appropriate.
    
2. **Normal Errors**: Slightly Skewed

3. **Constant Variance**: Seems Appropriate 

4. **Fixed X**: Mileage is accurate.

5. **Independent Errors**: the error terms are independent.


```{r}

par(mfrow=c(1,2))
plot(lmcd, which=1:2)
par(mfrow = c(1,1))
```




### Interpretation

**DHS Sedan 4D** Trim Model

$\underbrace{\hat{Y}_{ i }}_{Selling Price}=$ `r round(b[1],digits=0)` + `r round(b[2],digits=2)` $\underbrace{{ X }_{ i1 }}_{Mileage}$ Meaning: **Expected New Price = \$`r round(b[1],digits=0)`** and **Depreciation = \$`r round(b[2],digits=2)` per mile**

**DTS Sedan 4D** Trim Model

$\underbrace{\hat{Y}_{ i }}_{Selling Price}=$ `r round(b[1]+b[3],digits=0)` + `r round(b[2]+b[5],digits=2)` $\underbrace{{ X }_{ i1 }}_{Mileage}$ Meaning: **Expected New Price = \$`r round(b[1]+b[3],digits=0)`** and **Depreciation = \$`r round(b[2]+b[5],digits=2)` per mile**

**Sedan 4D** Trim Model

$\underbrace{\hat{Y}_{ i }}_{Selling Price}=$ `r round(b[1]+b[4],digits=0)` + `r round(b[2]+b[6],digits=2)` $\underbrace{{ X }_{ i1 }}_{Mileage}$ Meaning: **Expected New Price = \$`r round(b[1]+b[4],digits=0)`** and **Depreciation = \$`r round(b[2]+b[6],digits=2)` per mile**

```{r}
pander(lmcd)
```

**Conclusion**

1. With a **p-value≈`r summary(lmcd)$coefficients[2,4]`** on the slope for **DHS Sedan 4D**, we can be assured that depreciation for **DHS Sedan 4D** is not zero.

2. With a **p-value≈`r summary(lmcd)$coefficients[5,4]`** on the slope for **DTS Sedan 4D**, we can be assured that depreciation for **DTS Sedan 4D** is not the same as **DHS Sedan 4D**.

3. With a p-value of `r summary(lmcd)$coefficients[6,4]` on the slope for **Sedan 4D**, we can be assured that depreciation for **Sedan 4D** is not the same as **DHS Sedan 4D**.

I am convinced that the different Trim Styles of the Cadillac Deville have different Linear Depreciation Models. The DHS Model appears to have the highest new selling price and the fastest depreciation.


 

