---
title: "GSS Multiple Logistic Regression"
output: 
  html_document:
    theme: cerulean
    code_folding: hide
---

```{r Libraries, include=FALSE}
library(mosaic)
library(DT) 
library(knitr)
library(pander)
library(car)
library(plyr)
library(dplyr)
library(ResourceSelection)
#library(tidyverse)
```



```{r Datafix}
GSSslim<-read.csv("../Data/GSSslim11.csv", header=TRUE, stringsAsFactors = FALSE)

GSSguns<-subset(GSSslim, gunlaw==2 | gunlaw==1)

GSSguns$Oppose<-GSSguns$gunlaw-1


GSSguns$Female<-GSSguns$gender1-1

GSSguns<-GSSguns[c("age","Oppose","Female")]
```
## {.tabset .tabset-fade}

### Overview

"The General Social Survey (GSS) conducts basic scientific research on the structure and development of American society with a data-collection program designed to both monitor societal change within the United States and to compare the United States to other nations."[$^1$](http://www3.norc.org/GSS+Website/) It is a cooperative effort to survey the American people every couple years asking a wide variety of questions and has been going on since 1972. The 2012 data file is contained in the file `GSS2012.csv`.

[GSS Dataset](http://sda.berkeley.edu/sdaweb/analysis/?dataset=gss12)

### Analysis

For this analysis, I will explore this question:

<div style="padding-left:15px; font-weight:bold;">
Can a person's age and gender predict how they feel about requiring a permit to buy a gun? 
</div>

**AGE** Respondents Age

**Oppose** Would you favor or oppose a law which would require a person 
to obtain a police permit before he or she could buy a gun?

0. Favor
1. Oppose

**Female** Head of Household

0. Male
1. Female

Here is the data I will be using:

```{r Showdata}
datatable(GSSguns, extensions = "Responsive",options=list(lengthMenu = c(10,25,68)))
```


### Logistic Regression



```{r Logreg, warning=FALSE}
GSSg.glm <- glm(Oppose ~ age + Female + age:Female, data=GSSguns, family=binomial)
pander(summary(GSSg.glm))
b<-GSSg.glm$coefficients
pvLR<-coef(summary(GSSg.glm))[2,4]
```

See the end of this document for the interpretation on the results of this logistic regression.

### Appropriateness

Is Logistical Regression an appropriate model for taking age to predict how people feel about gun permits?

I want to test two things:

1. Does the model show that there is a Significant relationship between age and feelings?
2. Is Logistic Regression a Good Fit?

##### Significant

From the Logistic Regression, a p-value of **`r pvLR`** on slope shows that there is a signifcant relationship between age and feelings.

##### Goodness of Fit

Using the Hosmer and Lemeshow goodness of fit (GOF) test:

$$
H_0:\text{Logistical Model is Appropriate}\\H_a:\text{Logistical Model is Not Appropriate}
$$

```{r GOF, warning=FALSE}

pander(hoslem.test(GSSg.glm$y, GSSg.glm$fitted))
hlpv<-hoslem.test(GSSg.glm$y, GSSg.glm$fitted)$p.value

table(GSSguns$Oppose, GSSguns$age)


pander(hoslem.test(GSSg.glm$y, GSSg.glm$fitted))

summary(GSSg.glm)

#pchisq(1481.7, 1282, lower.tail = FALSE)
pchisq(1462.5, 1279, lower.tail = FALSE)
#pchisq(1481.7-1462.5, 3, lower.tail = FALSE)

```

The Hosmer-Lemeshow test will be used to test the goodness of fit of this logistic regression model. The null assumes the logistic regression is a good fit. As shown above, there is insufficient evidence to reject the null **p=`r hlpv`** so we will conclude a good logistic fit on these data.

### Graphics & Model

```{r Plot}
plot(Oppose ~ age, data=GSSguns, pch=16, cex=0.5, xlim=c(18,110), xlab= "Age", ylab="Oppose Gun Permits")

curve(exp(b[1] + b[2]*x)/(1+exp(b[1] + b[2]*x)),from=0, to=188,  add=TRUE, col='Blue')

curve(exp(b[1]+b[3] + (b[2]+b[4])*x)/(1+exp(b[1]+b[3] + (b[2]+b[4])*x)),from=0, to=188,  add=TRUE, col='red')

legend("right", legend=c("Male", "Female"), col=c("Blue","red"), lty=1)
```

$\quad Y_{i} = \text{Oppose}$
$\quad X_{i1} = \text{Age}$
$\quad X_{i2} = \left\{\begin{array}{ll} 1, & \text{if Gender} = \text{Female} \\ 0, & \text{if Gender} = \text{Male} \end{array}\right.$

$$\underbrace{Y_i}_{Oppose}=\beta_0+\beta_1\underbrace{X_{i1}}_{Age}+\beta_2\underbrace{X_{i2}}_{Female}+\beta_3{X_{i1}X_{i2}}+\epsilon_i $$

$\hat{ Y }_{ i }=$ `r b[1]` + `r b[2]` ${ X }_{ i1 }+$ `r b[3]` ${ X }_{ i2 }+$ `r b[4]` ${ X }_{ i1 }{ X }_{ i2 }$

As we are not interested in `age`, the hypotheses for this study will concern the coefficients of the various responses for `pray`.
$$
  H_0: \beta_1 = 0 \\
  H_a: \beta_1 \neq 0
$$

$$
  H_0: \beta_3 = 0 \\
  H_a: \beta_3 \neq 0
$$




### Interpretation

1. For males, the effect of `age` on the odds of opposing gun permits is $e^{`r b[2]`} = `r exp(b[2])`$ for every one year increase in age. This means there is a 1% drop in the odds of opposing gun permits for every year older.

2. Females are not significatly different than males.







