---
title: "Harmon Quiz Questions"
output: 
  html_document:
    theme: cerulean
    code_folding: hide
    #toc: true
    #toc_float: true
---

```{r, include=FALSE}
library(mosaic)
library(DT) 
library(knitr)
library(pander)
library(car)
library(plyr)
library(dplyr)
```



# Speed Quizzes {.tabset .tabset-fade}

## Movie Dataframe 

```{r}
mr4<-read.csv("./Data/mr4.csv", header=TRUE, stringsAsFactors = FALSE)
mr4[9:13]<-mr4[9:13]/1000000
pander(head(mr4))
```
## Week 1 

### Q1 

Use the mr4 dataset in R to compute the average score of and R-rated movie

```{r}
mean(score~rating, data = subset(mr4, rating == "R"))
```

### Q2 

Use the mr4 dataset in R, to create an appropriate graphic of R-Rated movie budgets.

```{r}
favstats(budget~rating, data = mr4)

boxplot(budget~rating, data = mr4)
```



### Q3 
Use the mr4 dataset in R to create an appropriate graphic that shows the growth in budget in movies over time. 
```{r}
plot(budget~year, data=mr4)

```



## Week 2

### Q1 

Use the mr4 dataset in R to compute the mean IMDB score of the different MPAA ratings.
```{r}
pander(mean(score~rating, data = mr4), caption = "Mean IMDB Score by Rating")
```



### Q2 

Use the mr4 dataset in R to make a graph that allows you to see how the budget is changes by year.

```{r}
plot(budget~year, data = mr4)
```



### Q3 
Run the following codes in R. Then select the statement that most appropriately interprets the resulting graph.
```{r}
palette(c("blue","red","green","purple"))

plot(budget ~ year, data=mr4, col=as.factor(rating), pch=16, xlab="Year", ylab="Budget in Millions", main="Movies 1986 to 2016")

legend("topleft", pch=16, legend=c("G","PG","PG-13","R"), title="MPAA Rating", bty='n', col=palette())
```

## Week 3

### Q1 

Use appropriate R commands and the mr4 dataset to determine which movie rating occurred 55 times in 1990.

```{r}
pander(table(mr4$rating, mr4$year == 1990))
```



### Q2 
Use the mr4 dataset in RStudio to test the following hypotheses.
$$
{ H }_{ 0 }:{ \mu  }_{\text{G Profit}}={ \mu  }_{\text{R Profit}}\\ { H }_{ a }:{ \mu  }_{\text{G Profit}}\neq{ \mu  }_{\text{R Profit}}
$$
```{r}
pander(t.test(Profit2017~rating, data = subset(mr4, rating %in% c("G","R")), mu = 0, alternative = "two.sided", conf.level = 0.95))
```

### Q3 
What two things are required to compute a p-value?

1. A test statistic 
2. sampling distribution of the test statistic

## Week 4

### Q1 

Use the mr4 dataset in R to find the number of R-rated movies from the UK in the dataset.
```{r}
pander(table(mr4$rating, mr4$country %in% "UK"))
```

### Q2 
Create an appropriate graphic using the mr4 dataset in R that would allow you to compare the distribution of Profit for Movies in each Rating.
```{r}
boxplot(Profit2017 ~ rating, data=mr4, ylab="Profit in millions", xlab="Rating", main="Profit by Rating")
```



### Q3 
Perform an appropriate Wilcoxon Test of the following hypotheses using the mr4 dataset in R.
$$
{ H }_{ 0 }:\quad { { Median }_{ G Profit }=Median }_{ R Profit }\\ { H }_{ a }:\quad { { Median }_{ G Profit }\neq Median }_{ R Profit }
$$
```{r}
pander(wilcox.test(Profit2017 ~ rating, data=subset(mr4, rating %in% c("G","R"))))
```

## Week 5

### Q3

In the mr4 dataset, what is the average length of G-Rated Movies released in 1990?

```{r}

pander(mean(runtime ~ rating, data=subset(mr4, year == "1990"), groups=year))

```

## Week 6

```{r}
pander(kruskal.test(salary~ rank, data=Salaries))
kruskal.test(salary~ rank, data=Salaries)
boxplot(salary~ rank, data=Salaries)
median(salary~ rank, data=Salaries)
```

## Week 7

```{r}
plot(Height ~ Volume, data=trees)
trees.lm <- lm(Height ~ Volume, data=trees)
abline(trees.lm)
summary(trees.lm)
trees.lm$coefficients

par(mfrow=c(1,2))
plot(trees.lm, which=1:2)
par(mfrow = c(1,1)) #This resets your plotting window for future plots.
```

```{r}

plot(waiting ~ eruptions, data=faithful)
of.lm <- lm(waiting ~ eruptions, data=faithful)
abline(of.lm)
pander(summary(of.lm))

par(mfrow=c(1,2))
plot(of.lm, which=1:2)
par(mfrow = c(1,1))
qqPlot(of.lm)

```

```{r}

plot(length ~ width, data=KidsFeet)
of.lm <- lm(length ~ width, data=KidsFeet)
abline(of.lm)
pander(summary(of.lm))

par(mfrow=c(1,2))
plot(of.lm, which=1:2)
par(mfrow = c(1,1))
qqPlot(of.lm)

```

## Week 8
```{r}
#boxplot(length~sex,data=mtcars)
lmcars <- lm(mpg ~ qsec + am + qsec:am, data=mtcars)
lmcars
summary(lmcars)
pander(lmcars)

par(mfrow=c(1,2))
plot(lmcars, which=1:2)
par(mfrow = c(1,1))

lmcars$coefficients
b<-lmcars$coefficients
palette(c("blue","red"))
plot(mpg ~ qsec,data=mtcars, col=as.factor(mtcars$am),pch=16)
abline(b[1], b[2], col="blue")
abline(b[1]+ b[3],b[2]+ b[4], col="red")
legend("topright",c("Automatic","Manual"), lty=1, lwd=5, col=palette(), cex=0.7, title="Transmission")
```

$$\underbrace{Y_i}_{mpg}=\beta_0+\beta_1\underbrace{X_{1i}}_{qsec}+\beta_2\underbrace{X_{2i}}_{am}+\beta_3\underbrace{X_{1i}X_{2i}}_{interaction}+\epsilon_i $$

$\hat{ Y }_{ i }=$ `r b[1]` + `r b[2]` ${ X }_{ 1i }+$ `r b[3]` ${ X }_{ 2i }+$ `r b[4]` ${ X }_{ 1i }{ X }_{ 2i }$
